---
title: ""
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
```

```{r}
library(readr)
library(tidyverse)
library(tidymodels)
library(kknn)
library(psych)
```

```{r}
ha <- read_csv("https://www.dropbox.com/s/aohbr6yb9ifmc8w/heart_attack.csv?dl=1")
```

```{r}
ha <- ha %>%
  mutate(
    sex = factor(sex),
    cp = factor(cp),
    restecg = factor(restecg),
    output = factor(output)
  ) %>%
  drop_na()
```

```{r}
hacv <- vfold_cv(ha, v = 15)
set.seed(10)

recipe1 <- recipe(output ~ cp + trtbps + chol + restecg, data = ha) %>% 
  step_normalize(all_numeric())

recipe2 <- recipe(output ~ cp + trtbps + sex + age, data = ha) %>% 
  step_normalize(all_numeric())

recipe3 <- recipe(output ~ cp + age + thalach + restecg, data = ha) %>% 
  step_normalize(all_numeric())
```

```{r}
knn <- nearest_neighbor(neighbors = tune()) %>% 
  set_engine("kknn") %>% 
  set_mode("classification")

knn_wflow <- workflow() %>% 
  add_model(knn) %>% 
  add_recipe(recipe2)

#k_grid = data.frame(k = seq(2, 30, by = 2))
k_grid <- grid_regular(neighbors(c(2, 50)), levels = 10)
set.seed(7)

knn_k <- knn_wflow %>% 
  tune_grid(resamples = hacv,
            grid = k_grid)

knn_k %>% show_best('roc_auc') 
```

```{r}
knn1 <- nearest_neighbor(neighbors = 44) %>% 
  set_engine("kknn") %>% 
  set_mode("classification")

knn_wflow <- workflow() %>% 
  add_model(knn1) %>% 
  add_recipe(recipe2)

knn_fit <- knn_wflow %>% 
  fit_resamples(hacv)


#knn_fit %>% collect_metrics()

knn_fit <- knn_wflow %>% 
  fit(ha)

preds <- knn_fit %>% 
   predict(ha)

ha_knn_pred <- ha %>% 
   mutate(prediction = preds$.pred_class)
```

```{r}
cohen.kappa(x=cbind(ha_knn_pred$prediction, ha_knn_pred$output))
```

Cohen’s Kappa turns out to be 0.52 for recipe1 which means based on the table we would say that the two raters only had a “moderate” level of agreement.

Cohen’s Kappa turns out to be 0.66 for recipe2 which means based on the table we would say that the two raters only had a “substantial” level of agreement.

Cohen’s Kappa turns out to be 0.5 for recipe3 which means based on the table we would say that the two raters only had a “substantial” level of agreement.

No the decision still remains the same for KNN. Recipe2 still has better metrics than others

```{r}
log <- logistic_reg() %>% 
  set_engine("glm") %>% 
  set_mode("classification")

log_wflow <- workflow() %>% 
  add_model(log) %>% 
  add_recipe(recipe3)

log_wflow %>% 
  fit_resamples(hacv)

log_fit <- log_wflow %>% 
  fit(ha)

log_pred <- predict(log_fit, ha)

log_ha <- ha %>% 
  mutate(preds = log_pred$.pred_class)

logmodel_fit <- log_fit %>% pull_workflow_fit()

logmodel_fit$fit %>% summary()
```

```{r}
cohen.kappa(x=cbind(log_ha$preds, log_ha$output))
```

Cohen’s Kappa turns out to be 0.5 for recipe1 which means based on the table we would say that the two raters only had a “substantial” level of agreement.

Cohen’s Kappa turns out to be 0.58 for recipe2 which means based on the table we would say that the two raters only had a “substantial” level of agreement.

Cohen’s Kappa turns out to be 0.51 for recipe3 which means based on the table we would say that the two raters only had a “substantial” level of agreement.

No the decision still remains the same for Logistic Regression. Recipe2 still has better metrics than others